---
title: "linear model from Web"
author: "javalos16"
date: "Put semester and year"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```
# Introduction

I will be utilize ANOVA to determine what model between Model 1, Model 2, and Model 3, to determine strength score based on arm and grip strength. I will be using three models, and the response variable as well as the numerical variable. I will be using the "num~num" helper file for this analysis.

## Model 1 SIM~ARMS

### Graphical results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(model.1,col='red')
```

As arm strength goes up, the simulation indicates that the sims goes up as well.


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation is O.69 which shows that arm strength is related to sims score. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

Both the intercept and the coefficient fo ARM strength are significantly different from 0.

### Prediction Interval



```{r}
newdata = data.frame(ARM=88,GRIP=94)
predict(model.1,newdata,interval="predict")
```

The prediction interval is from -1.7 to 3.1 for SIM score.


## Model 2 SIM~GRIP



### Graphical results

```{r}
model.1 <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(model.1,col='blue')
```

As grip strength goes up, the simulation indicates that the sims goes up as well.


### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation is O.64 which shows that arm strength is related to sim score. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```

Both the intercept and the coefficient fo grip strength are significantly different from 0.

### Prediction Interval



```{r}
newdata = data.frame(ARM=88,GRIP=94)
predict(model.1,newdata,interval="predict")
```

The prediction interval is from -1.7 to 3.1 for SIM score.

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Graphical results

```{r}
model.1 <- lm(SIMS~ARM+GRIP,data=data)
plot(SIMS~ARM,data=data)
abline(model.1,col='orange')
```

As arm plus grip strength goes up, the simulation indicates that the sims goes up as well.


### Numerical results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation is O.73 which shows that arm strength is related to sims score. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.1)
```

Both the intercept and the coefficient fo ARM strength are significantly different from 0.

### Prediction Interval



```{r}
newdata = data.frame(ARM=88,GRIP=94)
predict(model.1,newdata,interval="predict")
```

The prediction interval is from -1.7 to 3.1 for SIM score.



### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

